Notes on conformal manifolds

### 2025-05-22 Draft_MLFlatDirections.tex
update the draft

\paragraph{Potential}
The 22 scalars of the theory can be parametrised by ($22 = 32 - 10$, with 10 scalars gauge fixed using translations in the gauge group)
\begin{itemize}[label=\textbullet]
	\item $m = \nu\nu^{T}\in{\rm GL}(3,\mathbb{R})$ parametrizing the coset ${\rm GL}(3,\mathbb{R})/{\rm SO}(3)$,
	\item $\phi$ a $3\times3$ antisymmetric matrix,
	\item $\xi$ a $3\times4$ matrix, and $\xi^{2} = \xi \xi^{T}$,
	\item a dilaton $\tilde{\varphi}$.
\end{itemize}
We can further restrict ourselves to a set of 13 scalars (see ref.~\cite{Eloy:2021fhc}), with
\begin{equation}
	\begin{aligned}
		\xi &= \begin{pmatrix}
					0 & 0 & 0 & x_{1} \\
					0 & 0 & 0 & x_{2} \\
					0 & 0 & 0 & x_{3}
				\end{pmatrix},
		\quad
		\phi = \begin{pmatrix}
					0 & x_{4} & x_{5} \\
					-x_{4} & 0 & x_{6} \\
					-x_{5} & -x_{6} & 0
				\end{pmatrix},
		\quad
		\tilde{\varphi} = x_{13} \\[5pt]
		\nu &= e^{(6\,x_{7}+3\,x_{8}+\sqrt{3}\,x_{9})/6}
				\begin{pmatrix}
					1 & \frac{x_{10}}{\sqrt{2}} & \frac{x_{11}}{\sqrt{2}} + \frac{x_{10}x_{12}}{4} \\
					0 & e^{-x_{8}} & \frac{e^{-x_{8}}\,x_{12}}{\sqrt{2}} \\
					0 & 0 & e^{-(x_{8}+\sqrt{3}\,x_{9})/2}
				\end{pmatrix}.
	\end{aligned}
\end{equation}
Scalar potential from ref.~\cite{Eloy:2021fhc}:
%
\begin{equation} \label{eq:scalarpotential}
	\begin{aligned}
 		V & = 4\,e^{-4\tilde\varphi}+2\,e^{-2\tilde\varphi}\Big[-\tr\left(m+m^{-1}\right)+\tr\left(\phi m^{-1}\phi\right) -2\,\tr\left(\phi m^{-1}\xi^{2}\right)-2\,\tr\left(\xi^{2}\right)\\
 		&\qquad\quad-\tr\left(\xi^{2}m^{-1}\xi^{2}\right)  +\frac{1}{2}\,\det\left(m^{-1}\right)\left(1-\tr\left(\phi^{2}\right)-\tr\left(\xi^{4}\right)+\tr\left(\xi^{2}\right)^{2}\right) \\
 		&\qquad\quad +\frac{1}{2}\,{\rm T}\left(m^{-1}(\xi^{2}-\phi),(\xi^{2}+\phi)m^{-1},m+(\xi^{2}+\phi)m^{-1}(\xi^{2}-\phi)+2\,\xi^{2}\right)\\
 		&\qquad\quad +\frac{1}{4}\,{\rm T}\left(m^{-1},m+(\xi^{2}+\phi)m^{-1}(\xi^{2}-\phi)+2\,\xi^{2},m+(\xi^{2}+\phi)m^{-1}(\xi^{2}-\phi)+2\,\xi^{2}\right)\Big], 
 	\end{aligned}
\end{equation}
where ${\rm T}\left(A,B,C\right)=\varepsilon_{mnp}\,\varepsilon_{qrs}\,A^{mq}B^{nr}C^{ps}$.

As a first simplified example we have considered only the parameters $x_{1}, x_{2}, x_{4}, x_{8}$ and $x_{10}$. The potential~\eqref{eq:scalarpotential} becomes
\begin{equation} \label{eq:scalarpotential124810}
	\begin{aligned}
		V &= \frac{1}{8}\, e^{-2\,x_{8}} \bigg[4 + 4\,x_{1}^4 + e^{4\,x_{8}} \big(2 + x_{10}^2\big)^2 \big(1 + x_{2}^4\big)\\
		  & \quad\qquad\qquad - 4\,e^{3\,x_{8}}\,\big(2 + x_{10}^2\big) \Big(2 - x_{1}^2 + \sqrt{2}\,x_{1} x_{10} x_{2}^3 + x_{2}^4 + 
      			2\,x_{1} x_{2} x_{4} + x_{4}^2 - x_{2}^2 \big(1 - x_{1}^2 + x_{4}^2\big)\Big)\\
        & \quad\qquad\qquad - 8\,e^{x_{8}}\,\Big(2 + x_{1}^4 + \sqrt{2}\,x_{1}^3 x_{10} x_{2} - x_{2}^2 - 2\,x_{1} x_{2} x_{4} + 
      			x_{4}^2 - x_{1}^2 \big(1 - x_{2}^2 + x_{4}^2\big)\Big)\\
        & \quad\qquad\qquad + 4\,e^{2\,x_{8}}\,\Big(2 - 4\,x_{1}^2 + x_{1}^4 - 4\,x_{2}^2 + 4\,x_{1}^2 x_{2}^2 + x_{2}^4
        			+ x_{10}^2\big(1 + 3\,x_{1}^2 x_{2}^2\big) + 4\,x_{4}^2 + x_{4}^4\Big)\\
        & \quad\qquad\qquad + 8\sqrt{2}\,x_{10}\,e^{2\,x_{8}}\,\Big(x_{1}^3 x_{2} + x_{1}^2 x_{4} - x_{2}^2 x_{4} + x_{1} \big(x_{2}^3 - x_{2} x_{4}^2\big)\Big)\bigg].
	\end{aligned}
\end{equation}
\ce{Change notation to keep $x$ for the polynomial variables?}

@@

		We then perform gradient descent on the points using TensorFlow’s automatic differentiation. The loss function is defined as:
		\begin{equation}
			\mathcal{L} = \sum_{i = 1}^{n_{points}} || \nabla V(\vec{x}^{,i})||^2
		\end{equation}
		where $\vec{x}^{,i} = (x^i_1,x^i_2,x^i_4,x^i_8,x^i_{10})$ denotes the data points.

@@

		\begin{figure}[t]
			\centering
			\includegraphics[scale = 0.25]{Figures/triangular_plot_1_2_4_8_10.png} %names need to be changed.
			\caption{Triangular plot showing $2d$ projections and $1d$ histograms of the data after the gradient descent}
			\label{triangular_plot_1_2_4_8_10}
		\end{figure}

		We can make a few comments on those plots. First, we observe non-trivial correlations in the data. Some of these may result from larger basins of attraction, such as in the $x_1/x_2$ plot. However, the structures seen in the $x_4/x_8$ or $x_4/x_{10}$ plots likely reflect genuine features of the manifold, and will show latter that this is indeed the case. We also note that alll directions appear to be well populated. 
		%Furthermore, we can notice that a large majority of the points converge to the origin $\vec{0}$. This is not surprising, as this just mean that the round sphere solution has a larger basin of attraction, which sounds reasonable. We do not however attempt to shift the points along flat directions to depopulate the origin or repopulate other regions.

@@

		We set the minimum cluster size to 10 points. Out of the 986,060 3-dimensional points, the algorithm identifies three clusters: one of size 10, one of size 91,747, and one of size 6,849. \ce{Are those numbers right? We loose more than 800,000 points?}

@@

		Now we have sampled the manifold and extracted some basic information about it (namely its dimension and the fact that it is made of one block), we would like to see if we can extract some analytic formula to characterise it. What we have at the moment, are points on a 3-dimensional manifold, which are embedded in a 5-dimensional space. Therefore we can conclude that, in order to characterise the manifold, we need two constraints on the embedding coordinates $\vec{x} = (x_1,x_2,x_4,x_8,x_{10})$. If we have a look at the form of the potential \eqref{eq:scalarpotential124810}, we see that if we use $\tilde{x}_{8} = e^{x_8}$, that, up to a global $e^{-2x_8}$ factor, this potential is actually a polynomial of the embedding coordinates. Therefore, the components of $|\nabla V|$ are also polynomials in those variables. We conclude that the constraints on the embedding coordinates we are looking for are polynomial constraints of the form $p(\vec{x}) = 0$, and that there are two of those. Of course if one takes directly the gradient of \eqref{eq:scalarpotential124810}, one ends up with such conditions, but none are usable directly to solve for two of the variables in terms of the others. The problem we are facing here is therefore a problem of symbolic regression: we are looking for analytic expressions (polynomial) that vanish once evaluated on our data points. There are a number of way one can deal with it, using already existing methods such as AI Feynman methods~\cite{Udrescu:2019mnk}, or ..., or by doing rough gradient descent on the most general polynomial with arbitrary coefficients and trying to minimize its value once evaluated on the data points. In the spirit of trying to build a generalisable method, we develop here our own method, which is based on symbolic regression using an Annealing Importance Sampling method.

@@

	\paragraph{Results}
	We have used the numerical analysis outlined in the previous sections to the search for extrema of the scalar potential~\eqref{eq:scalarpotential124810}. The code finds the 7 different following polynomials: \ce{Mention that we ``rounded'' the coefficients to integer and square root of them.}
	\begin{subequations} \label{eq:pols}
    \begin{align}
      p_{1} &= -\sqrt{2}\,x_{1} + \sqrt{2}\,x_{1}\tilde{x}_{8} + x_{2}\tilde{x}_{8}x_{10} - \sqrt{2}\,x_{2}x_{4}\tilde{x}_{8},\\
      p_{2} &= 2\,x_{2} - 2\,x_{2}\tilde{x}_{8} + \sqrt{2}\,x_{1}x_{10} + 2\,x_{1}x_{4} - x_{2}\tilde{x}_{8}x_{10}^{2},\\
      p_{3} &= 2\,x_{2} - 2\,x_{2}\tilde{x}_{8} + \sqrt{2}\,x_{1}\tilde{x}_{8}x_{10} + 2\,x_{1}x_{4}\tilde{x}_{8}
      		- 2\,x_{2} x_{4}^{2}\tilde{x}_{8},\\
      p_{4} &= \sqrt{2}\,x_{2} - \sqrt{2}\,x_{2}\tilde{x}_{8} + \sqrt{2}\,x_{1}\,x_{4} + x_{1}\tilde{x}_{8}x_{10}
      		- x_{2}x_{4}\tilde{x}_{8}x_{10},\\
      p_{5} &= -2\,x_{1} - 2\,x_{2}x_{4}- 2\,x_{1}x_{4}^{2} + 2\,x_{1}\tilde{x}_{8} + \sqrt{2}\,x_{2}x_{10}
      		+ x_{1}\tilde{x}_{8}x_{10}^{2},\\
      p_{6} &= -2\,x_{2}x_{4} - 2\,x_{1}x_{4}^{2} + 2\,x_{2}x_{4}\tilde{x}_{8} + \sqrt{2}\,x_{2}x_{10} 
      		- \sqrt{2}\,x_{2}\tilde{x}_{8}x_{10} +  x_{1}\tilde{x}_{8}x_{10}^{2},\\
      p_{7} &= -\sqrt{2}\,x_{1}^{2}x_{4} + \sqrt{2}\,x_{2}^{2}x_{4} + \sqrt{2}\,x_{1}x_{2}x_{4}^{2} - x_{1}^{2}x_{10}
      		- x_{2}^{2}x_{10},
    \end{align}
  \end{subequations}
  where $\tilde{x}_{8} = e^{x_{8}}$. They are found with different frequencies, depending on the chosen parameters.

@@

	  Mean loss with regularisation for particles reproducing a target: $597 \pm 264$

	  Mean loss without regularisation for particles reproducing a target: $345 \pm 246$
  		\item For 100 runs with parameters
		\begin{equation}
			\begin{gathered}
				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{5}, \quad \sigma = 0.1, \\
				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
			\end{gathered}
		\end{equation}
		the polynomials are found at the following frequencies
	  \begin{equation}
	  	\begin{tabular}{l|cccccccc}
	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
	  		Frequency & 69\% & 11\% & 7\% & 12\% & 0\% & 4\% & 0\% & 13\%
	  	\end{tabular}
	  \end{equation}
	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample10000beta5}.

@@

	  Mean loss with regularisation for particles reproducing a target: $606 \pm 257$

	  Mean loss without regularisation for particles reproducing a target: $359 \pm 244$

@@

	  Mean loss with regularisation for particles reproducing a target: $854 \pm 427$

	  Mean loss without regularisation for particles reproducing a target: $602 \pm 417$

	  \begin{figure}[h!]
	  	\centering
	  	\begin{tikzpicture}
	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_19_at_06_01_21.pdf}};
	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_19_at_06_01_21_detailed.pdf}};
	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
	  	\end{tikzpicture}
	  	\caption{(a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta3}. (b) Evolution of the mean numbers of particles reproducing each targets polynomial. The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
	  	\label{fig:sample10000beta3}
	  \end{figure}

	  \item For 100 runs with parameters
		\begin{equation} \label{eq:sample10000beta3sigmavar}
			\begin{gathered}
				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{3}, \quad \sigma = 0.5 - \frac{0.45}{1+\exp\big(10-20 i/n_{\rm iter}\big)}, \\
				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
			\end{gathered}
		\end{equation}
		the polynomials are found at the following frequencies
	  \begin{equation}
	  	\begin{tabular}{l|cccccccc}
	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
	  		Frequency & 68\% & 17\% & 6\% & 9\% & 2\% & 1\% & 1\% & 11\%
	  	\end{tabular}
	  \end{equation}
	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample10000beta3sigmavar}.

	  Averaged number of particles reproducing a target in a successful run: $966 \pm 115$

	  Mean loss with regularisation for particles reproducing a target: $837 \pm 438$

	  Mean loss without regularisation for particles reproducing a target: $609 \pm 430$

	  \begin{figure}[h!]
	  	\centering
	  	\begin{tikzpicture}
	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_21_at_11_52_46.pdf}};
	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_21_at_11_52_46_detailed.pdf}};
	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
	  	\end{tikzpicture}
	  	\caption{(a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta3sigmavar}. (b) Evolution of the mean numbers of particles reproducing each targets polynomial. The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
	  	\label{fig:sample10000beta3sigmavar}
	  \end{figure}

@@

	  \begin{figure}[h!]
	  	\centering
	  	\begin{tikzpicture}
	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_20_at_08_01_44.pdf}};
	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_20_at_08_01_44_detailed.pdf}};
	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
	  	\end{tikzpicture}
	  	\caption{(a) Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample1000}. (b) Evolution of the mean numbers of particles reproducing each targets polynomial. The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
	  	\label{fig:sample1000}
	  \end{figure}
  \end{enumerate}

>>>>

\paragraph{Potential}
The 22 scalars of the theory can be parametrised by ($22 = 32 - 10$, with 10 scalars gauge fixed using translations in the gauge group)
\begin{itemize}[label=\textbullet]
	\item $m = \nu\nu^{T}\in{\rm GL}(3,\mathbb{R})$ parametrizing the coset ${\rm GL}(3,\mathbb{R})/{\rm SO}(3)$,
	\item $\phi$ a $3\times3$ antisymmetric matrix,
	\item $\xi$ a $3\times4$ matrix, and $\xi^{2} = \xi \xi^{T}$,
	\item a dilaton $\tilde{\varphi}$.
\end{itemize}
We can further restrict ourselves to a set of 13 scalars (see ref.~\cite{Eloy:2021fhc}), with
\begin{equation}
	\begin{aligned}
		\xi &= \begin{pmatrix}
					0 & 0 & 0 & x_{1} \\
					0 & 0 & 0 & x_{2} \\
					0 & 0 & 0 & x_{3}
				\end{pmatrix},
		\quad
		\phi = \begin{pmatrix}
					0 & x_{4} & x_{5} \\
					-x_{4} & 0 & x_{6} \\
					-x_{5} & -x_{6} & 0
				\end{pmatrix},
		\quad
		\tilde{\varphi} = x_{13} \\[5pt]
		\nu &= e^{(6\,x_{7}+3\,\tilde{x}_{8}+\sqrt{3}\,x_{9})/6}
				\begin{pmatrix}
					1 & \frac{x_{10}}{\sqrt{2}} & \frac{x_{11}}{\sqrt{2}} + \frac{x_{10}x_{12}}{4} \\
					0 & e^{-\tilde{x}_{8}} & \frac{e^{-\tilde{x}_{8}}\,x_{12}}{\sqrt{2}} \\
					0 & 0 & e^{-(\tilde{x}_{8}+\sqrt{3}\,x_{9})/2}
				\end{pmatrix}.
	\end{aligned}
\end{equation}
Scalar potential from ref.~\cite{Eloy:2021fhc}:
%
\begin{equation} \label{eq:scalarpotential}
	\begin{aligned}
 		V & = 4\,e^{-4\tilde\varphi}+2\,e^{-2\tilde\varphi}\Big[-\tr\left(m+m^{-1}\right)+\tr\left(\phi m^{-1}\phi\right) -2\,\tr\left(\phi m^{-1}\xi^{2}\right)-2\,\tr\left(\xi^{2}\right)\\
 		&\qquad\quad-\tr\left(\xi^{2}m^{-1}\xi^{2}\right)  +\frac{1}{2}\,\det\left(m^{-1}\right)\left(1-\tr\left(\phi^{2}\right)-\tr\left(\xi^{4}\right)+\tr\left(\xi^{2}\right)^{2}\right) \\
 		&\qquad\quad +\frac{1}{2}\,{\rm T}\left(m^{-1}(\xi^{2}-\phi),(\xi^{2}+\phi)m^{-1},m+(\xi^{2}+\phi)m^{-1}(\xi^{2}-\phi)+2\,\xi^{2}\right)\\
 		&\qquad\quad +\frac{1}{4}\,{\rm T}\left(m^{-1},m+(\xi^{2}+\phi)m^{-1}(\xi^{2}-\phi)+2\,\xi^{2},m+(\xi^{2}+\phi)m^{-1}(\xi^{2}-\phi)+2\,\xi^{2}\right)\Big], 
 	\end{aligned}
\end{equation}
where ${\rm T}\left(A,B,C\right)=\varepsilon_{mnp}\,\varepsilon_{qrs}\,A^{mq}B^{nr}C^{ps}$.

As a first simplified example we have considered only the parameters $x_{1}, x_{2}, x_{4}, \tilde{x}_{8}$ and $x_{10}$. The potential~\eqref{eq:scalarpotential} becomes
\begin{equation} \label{eq:scalarpotential124810}
	\begin{aligned}
		V &= \frac{1}{8}\, e^{-2\,\tilde{x}_{8}} \bigg[4 + 4\,x_{1}^4 + e^{4\,\tilde{x}_{8}} \big(2 + x_{10}^2\big)^2 \big(1 + x_{2}^4\big)\\
		  & \quad\qquad\qquad - 4\,e^{3\,\tilde{x}_{8}}\,\big(2 + x_{10}^2\big) \Big(2 - x_{1}^2 + \sqrt{2}\,x_{1} x_{10} x_{2}^3 + x_{2}^4 + 
      			2\,x_{1} x_{2} x_{4} + x_{4}^2 - x_{2}^2 \big(1 - x_{1}^2 + x_{4}^2\big)\Big)\\
        & \quad\qquad\qquad - 8\,e^{\tilde{x}_{8}}\,\Big(2 + x_{1}^4 + \sqrt{2}\,x_{1}^3 x_{10} x_{2} - x_{2}^2 - 2\,x_{1} x_{2} x_{4} + 
      			x_{4}^2 - x_{1}^2 \big(1 - x_{2}^2 + x_{4}^2\big)\Big)\\
        & \quad\qquad\qquad + 4\,e^{2\,\tilde{x}_{8}}\,\Big(2 - 4\,x_{1}^2 + x_{1}^4 - 4\,x_{2}^2 + 4\,x_{1}^2 x_{2}^2 + x_{2}^4
        			+ x_{10}^2\big(1 + 3\,x_{1}^2 x_{2}^2\big) + 4\,x_{4}^2 + x_{4}^4\Big)\\
        & \quad\qquad\qquad + 8\sqrt{2}\,x_{10}\,e^{2\,\tilde{x}_{8}}\,\Big(x_{1}^3 x_{2} + x_{1}^2 x_{4} - x_{2}^2 x_{4} + x_{1} \big(x_{2}^3 - x_{2} x_{4}^2\big)\Big)\bigg].
	\end{aligned}
\end{equation}
\ce{Change notation to keep $x$ for the polynomial variables?}

@@

		We then perform gradient descent on the points using TensorFlow’s automatic differentiation. The loss function is defined as:
		\begin{equation}
			\mathcal{L} = \sum_{i = 1}^{n_{points}} || \nabla V(\vec{x}^{,i})||^2
		\end{equation}
		where $\vec{x}^{\,i} = (x^i_1,x^i_2,x^i_4,\tilde{x}^i_8,x^i_{10})$ denotes the data points.

@@

		\begin{figure}[t]
			\centering
			\includegraphics[scale = 0.3]{Figures/triangular_plot_1_2_4_8_10_new.png} %names need to be changed.
			\caption{Triangular plot showing $2d$ projections and $1d$ histograms of the data after the gradient descent}
			\label{triangular_plot_1_2_4_8_10}
		\end{figure}

		We can make a few comments on those plots. First, we observe non-trivial correlations in the data. Some of these may result from larger basins of attraction, such as in the $x_1/x_2$ plot. However, the structures seen in the $x_4/\tilde{x}_8$ or $x_4/x_{10}$ plots likely reflect genuine features of the manifold, and will show latter that this is indeed the case. We also note that alll directions appear to be well populated. 
		%Furthermore, we can notice that a large majority of the points converge to the origin $\vec{0}$. This is not surprising, as this just mean that the round sphere solution has a larger basin of attraction, which sounds reasonable. We do not however attempt to shift the points along flat directions to depopulate the origin or repopulate other regions.

@@

		We set the minimum cluster size to 10 points. Out of the 98,606 3-dimensional points, the algorithm identifies three clusters: one of size 10, one of size 91,747, and one of size 6,849.

@@

		Now we have sampled the manifold and extracted some basic information about it (namely its dimension and the fact that it is made of one block), we would like to see if we can extract some analytic formula to characterise it. What we have at the moment, are points on a 3-dimensional manifold, which are embedded in a 5-dimensional space. Therefore we can conclude that, in order to characterise the manifold, we need two constraints on the embedding coordinates $\vec{x} = (x_1,x_2,x_4,\tilde{x}_8,x_{10})$. If we have a look at the form of the potential \eqref{eq:scalarpotential124810}, we see that if we use $x_{8} = e^{\tilde{x}_8}$, that, up to a global $e^{-2\tilde{x}_8}$ factor, this potential is actually a polynomial of the embedding coordinates. Therefore, the components of $|\nabla V|$ are also polynomials in those variables. We conclude that the constraints on the embedding coordinates we are looking for are polynomial constraints of the form $p(\vec{x}) = 0$, and that there should be at least two of those. Note that we are now taking $\vec{x} = (x_1,x_2,x_4,\tilde{x}_8,x_{10})$. Of course if one takes directly the gradient of \eqref{eq:scalarpotential124810}, one ends up with such conditions, but none are usable directly to solve for two of the variables in terms of the others. The problem we are facing here is therefore a problem of symbolic regression: we are looking for analytic expressions (polynomial) that vanish once evaluated on our data points. There are a number of way one can deal with it, using already existing methods such as AI Feynman methods~\cite{Udrescu:2019mnk}, or ..., or by doing rough gradient descent on the most general polynomial with arbitrary coefficients and trying to minimize its value once evaluated on the data points. In the spirit of trying to build a generalisable method, we develop here our own method, which is based on symbolic regression using an Annealing Importance Sampling method.

@@

	\paragraph{Results}
	We have used the numerical analysis outlined in the previous sections to the search for extrema of the scalar potential~\eqref{eq:scalarpotential124810}. The code finds the 7 different following polynomials: \ce{Mention that we ``rounded'' the coefficients to integer and square root of them.}
	\begin{subequations} \label{eq:pols}
    \begin{align}
      p_{1} &= -\sqrt{2}\,x_{1} + \sqrt{2}\,x_{1}\tilde{x}_{8} + x_{2}\tilde{x}_{8}x_{10} - \sqrt{2}\,x_{2}x_{4}\tilde{x}_{8},\\
      p_{2} &= 2\,x_{2} - 2\,x_{2}\tilde{x}_{8} + \sqrt{2}\,x_{1}x_{10} + 2\,x_{1}x_{4} - x_{2}\tilde{x}_{8}x_{10}^{2},\\
      p_{3} &= 2\,x_{2} - 2\,x_{2}\tilde{x}_{8} + \sqrt{2}\,x_{1}\tilde{x}_{8}x_{10} + 2\,x_{1}x_{4}\tilde{x}_{8}
      		- 2\,x_{2} x_{4}^{2}\tilde{x}_{8},\\
      p_{4} &= \sqrt{2}\,x_{2} - \sqrt{2}\,x_{2}\tilde{x}_{8} + \sqrt{2}\,x_{1}\,x_{4} + x_{1}\tilde{x}_{8}x_{10}
      		- x_{2}x_{4}\tilde{x}_{8}x_{10},\\
      p_{5} &= -2\,x_{1} - 2\,x_{2}x_{4}- 2\,x_{1}x_{4}^{2} + 2\,x_{1}\tilde{x}_{8} + \sqrt{2}\,x_{2}x_{10}
      		+ x_{1}\tilde{x}_{8}x_{10}^{2},\\
      p_{6} &= -2\,x_{2}x_{4} - 2\,x_{1}x_{4}^{2} + 2\,x_{2}x_{4}\tilde{x}_{8} + \sqrt{2}\,x_{2}x_{10} 
      		- \sqrt{2}\,x_{2}\tilde{x}_{8}x_{10} +  x_{1}\tilde{x}_{8}x_{10}^{2},\\
      p_{7} &= -\sqrt{2}\,x_{1}^{2}x_{4} + \sqrt{2}\,x_{2}^{2}x_{4} + \sqrt{2}\,x_{1}x_{2}x_{4}^{2} - x_{1}^{2}x_{10}
      		- x_{2}^{2}x_{10},
    \end{align}
  \end{subequations}
  where $x_{8} = e^{\tilde{x}_{8}}$. They are found with different frequencies, depending on the chosen parameters.

@@

	  Mean loss with regularisation for particles reproducing a target: $285 \pm 108$

	  Mean loss without regularisation for particles reproducing a target: $33 \pm 24$
  		\item For 100 runs with parameters
		\begin{equation}
			\begin{gathered}
				\texttt{max degree} = 4, \quad \texttt{max num monomials} = 6, \quad n_{\rm iter} = 1000, \quad n_{\rm particles} = 1000, \\
				\texttt{sample size} = 10000, \quad {\rm reg} = 10^{3}, \quad \beta = 10^{-10} + \left(\frac{i}{n_{\rm iter}}\right)^{5}, \quad \sigma = 0.1, \\
				p_{\rm add} = 0, \quad p_{\rm remove} = 0, \quad p_{\rm modify} = 0.5, \quad p_{\rm multiply} = 0.25, \quad p_{\rm divide} = 0.25,
			\end{gathered}
		\end{equation}
		the polynomials are found at the following frequencies
	  \begin{equation}
	  	\begin{tabular}{l|cccccccc}
	  		& $p_{1}$ & $p_{2}$ & $p_{3}$ & $p_{4}$ & $p_{5}$ & $p_{6}$ & $p_{7}$ & $\varnothing$ \\\hline\hline
	  		Frequency & 69\% & 11\% & 7\% & 12\% & 0\% & 4\% & 0\% & 13\%
	  	\end{tabular}
	  \end{equation}
	  The dynamics of the appearance of the target polynomials is plotted in fig.~\ref{fig:sample10000beta5}.

@@

	  Mean loss with regularisation for particles reproducing a target: $282 \pm 91$

	  Mean loss without regularisation for particles reproducing a target: $35 \pm 24$

@@

	  Mean loss with regularisation for particles reproducing a target: $310 \pm 115$

	  Mean loss without regularisation for particles reproducing a target: $58 \pm 40$

	  \begin{figure}[h!]
	  	\centering
	  	\begin{tikzpicture}
	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_19_at_06_01_21.pdf}};
	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_19_at_06_01_21_detailed.pdf}};
	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
	  	\end{tikzpicture}
	  	\caption{Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample10000beta3}. (b) Evolution of the mean numbers of particles reproducing each targets polynomial. The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
	  	\label{fig:sample10000beta3}
	  \end{figure}

@@

	  \begin{figure}[h!]
	  	\centering
	  	\begin{tikzpicture}
	  		\draw (0,0) node (fig1) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_20_at_08_01_44.pdf}};
	  		\draw ($(fig1.north west) + (0,0)$) node {\small (a)};
	  		\draw (0,-8) node (fig2) {\includegraphics[scale=0.75]{Figures/Count_beta_history_2025_05_20_at_08_01_44_detailed.pdf}};
	  		\draw ($(fig2.north west) + (0,0)$) node {\small (b)};
	  	\end{tikzpicture}
	  	\caption{Evolution of the mean numbers of particles reproducing a target polynomials and its $1\sigma$ deviation for the parameters~\eqref{eq:sample1000}. (b) Evolution of the mean numbers of particles reproducing each targets polynomial. The vertical lines indicate when there are an average 5 particles reproducing a given polynomial, and the value of $\beta$ at that moment.}
	  	\label{fig:sample1000}
	  \end{figure}
  \end{enumerate}
